CODE CHECK

### 2020-06-02 codecheck-paper.Rmd
Update codecheck-paper.Rmd

- role of data and code, data science
- reproducible resarch
- data enclaves
- CASCAID
- ROpenSci/PyOpenSci (and how their software review differs, though they also collaborate with journals, https://devguide.ropensci.org/softwarereviewintro.html)
- time capsules > https://twitter.com/DougBlank/status/1135904909663068165?s=09
- science is changing: https://theconversation.com/what-you-need-to-know-about-how-coronavirus-is-changing-science-137641

@@

- need publishers build up data science experts who can conduct checks?
- integration of software/data citation checks benefitial?
- bot-support and tools (linter)
- how can open platforms be used to enable a review in private (cf. https://www.cambridge.org/core/blog/2019/08/19/how-to-make-the-data-and-code-for-your-manuscript-available-to-peer-reviewers-before-making-it-public/), if that is desired
- Does nudging towards better practices work (highlight the successes) or is any check with opt-in doomed to fail?
- Do we need more than one codechecker? Is there a similar diversity as in a peer review where more opinions are needed?
- can CODE CHECK work for preprints? how? is a re-check required?
- risk: is the hurdle too low? are "levels" of checks are solution to increase transparency of check's level of detail
- code check in the context of innovations and disruptions in scientific publishing
  - https://doi.org/10.1042/ETLS20180172
  - https://doi.org/10.3390/publications7020034
- should every code be checkd, or should the labour be capped by only checking "important" works or at important stages; if yes, isn't peer review such a stage?
- see https://github.com/codecheckers/discussion
- can we establish code checks as a type of review within the schol comm metadata (or should we?) > we should not, put them on the same level as reviews!

>>>>

- role of data and code, data science
- reproducible resarch
- data enclaves
- CASCAID
- ROpenSci/PyOpenSci (and how their software review differs, though they also collaborate with journals, https://devguide.ropensci.org/softwarereviewintro.html)
- time capsules > https://twitter.com/DougBlank/status/1135904909663068165?s=09
- science is changing: https://theconversation.com/what-you-need-to-know-about-how-coronavirus-is-changing-science-137641
- reproducibility is important, also
  - effects on well-being/mental health, https://www.nature.com/articles/d41586-020-01642-9

@@

- need publishers build up data science experts who can conduct checks?
- integration of software/data citation checks benefitial?
- bot-support and tools (linter)
- how can open platforms be used to enable a review in private (cf. https://www.cambridge.org/core/blog/2019/08/19/how-to-make-the-data-and-code-for-your-manuscript-available-to-peer-reviewers-before-making-it-public/), if that is desired
- Does nudging towards better practices work (highlight the successes) or is any check with opt-in doomed to fail?
- Do we need more than one codechecker? Is there a similar diversity as in a peer review where more opinions are needed?
- can CODE CHECK work for preprints? how? is a re-check required?
- risk: is the hurdle too low? are "levels" of checks are solution to increase transparency of check's level of detail
- code check in the context of innovations and disruptions in scientific publishing
  - https://doi.org/10.1042/ETLS20180172
  - https://doi.org/10.3390/publications7020034
- should every code be checkd, or should the labour be capped by only checking "important" works or at important stages; if yes, isn't peer review such a stage?
- see https://github.com/codecheckers/discussion
- can we establish code checks as a type of review within the schol comm metadata (or should we?) > we should not, put them on the same level as reviews!
- how can we turn a CODECHECK into a positive experience?
  - cf. kindness in peer review in https://www.mdpi.com/2304-6775/8/2/26
